Symmetric Peer-to-Peer Applications

### 2022-08-19 tpd-22.tex
- algos
- table.png

In this section, we revisit existing solutions for symmetric distributed
applications.
We focus on (i) how the network is organized, (ii) how events are propagated,
and (iii) how global time is determined.
Figure~\ref{fig.table} compares selected works regarding these aspects.

@@

An antagonistic approach to computing a series of event occurrences
deterministically, is to model the application data structures with
conflict-free replicated data types (CRDTs)~\cite{TODO}.
CRDTs must be designed in such a way that all operations are commutative, so
that the order in which they are applied does not affect the final outcome.
%
As detailed in Figure~\ref{fig.algos}, peers can communicate operations
directly to each other with no central authority.
Also, since operations need not to be ordered, they can be applied at the
very first moment they are generated or received, even if the peers are
offline.
%
Since operations must be commutative, it is not possible to timestamp them
in a global shared clock.
Hence, there is no notion of a timeline with peers going through bit-identical
steps, but they do eventually reach the same state.
%
On the one hand, the main advantage of CRDTs is they support the concept of
local-first software~\cite{TODO}, since they work offline.
On the other hand, they provide very restrictive APIs (the CRDTs themselves),
and do not support real-time consensus among peers.
%
Automerge~\cite{TODO} along with its accompanying Hypermerge peer-to-peer
infrastructure is an example of an implementation of this approach.

@@

\section{The API \& Middleware}
\label{sec.conclusion}

\section{Evaluation}
\label{sec.conclusion}

@@

\bibliographystyle{IEEEtran}
\bibliography{tpd-22}

%\begin{comment}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{chico}}]{Francisco Sant'Anna}
received his PhD degree in Computer Science from PUC-Rio, Brazil in
2013.
In 2016, he joined the Faculty of Computer Science at the Rio de Janeiro State
University, Brazil.
His research interests include Programming Languages and Concurrent \&
Distributed Systems.
\end{IEEEbiography}
%\end{comment}

>>>>

% docs.google.com/spreadsheets/d/1CpMmEgabJq2XQeTDW_BNCV4JWrcMlELuaEjDtw7kwg0/
\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{table}
  \caption{
    \label{fig.table}
  }
\end{figure}

\begin{figure*}[t]
  \centering
  \includegraphics[width=\linewidth]{algos}
  \caption{
    \label{fig.algos}
  }
\end{figure*}

In this section, we revisit existing solutions for symmetric distributed
applications.
We focus on (i) how the network is organized, (ii) how global time is
determined, and (iii) how events are propagated.
Figure~\ref{fig.table} compares selected works regarding these aspects.

@@

An antagonistic approach to deterministic reactions to events is to model the
application data structures with conflict-free replicated data types
(CRDTs)~\cite{TODO}.
CRDTs are designed in such a way that all operations are commutative, so that
the order in which they are applied does not affect the final outcome.
%
As detailed in Figure~\ref{fig.algos}, peers can communicate operations
directly to each other with no central authority.
Also, since operations need not to be ordered, they can be applied at the
very first moment they are generated or received, even if the peers are
offline.
%
Since operations must be commutative, it is not possible to timestamp them
in a global shared clock.
Hence, there is no notion of a timeline with peers going through bit-identical
steps, but they do eventually reach the same state.
%
On the one hand, the main advantage of CRDTs is they support the concept of
local-first software~\cite{TODO}, since they work offline.
On the other hand, they provide very restrictive APIs (the CRDTs themselves),
and do not support real-time consensus among peers.
%
Automerge~\cite{TODO} along with its accompanying Hypermerge peer-to-peer
infrastructure is an example of an implementation of this approach.

In this work, we try to .

@@

\section{The API \& Middleware}
\label{sec.api}

\section{Evaluation}
\label{sec.eval}

@@

\bibliographystyle{IEEEtran}
%\bibliography{tpd-22}

\begin{comment}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{chico}}]{Francisco Sant'Anna}
received his PhD degree in Computer Science from PUC-Rio, Brazil in
2013.
In 2016, he joined the Faculty of Computer Science at the Rio de Janeiro State
University, Brazil.
His research interests include Programming Languages and Concurrent \&
Distributed Systems.
\end{IEEEbiography}
\end{comment}
